\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN250}), respectively. This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).

>>>>

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively. This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on the tip velocity).

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s). Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution. Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10_VN150}
\end{figure}

@@

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) map of permeabilities \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) distribution of permeability ({\bf K}) field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation. Saturation map is the same as used in Fig.\red{XX ... is it true??}. The domain contains \red{XXXX} elements.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_c}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_d}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\hbox{\includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
       \includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}). \blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10_VN250}
\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s). Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution. Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10_VN150}
\end{figure}
\end{landscape}

@@

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) map of permeabilities \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) distribution of permeability ({\bf K}) field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation. The domain contains elements.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while a second region/inlet is introduced. For $t=0.101$s, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps. For this simulation there are $13226$ elements for the fixed messh and $43716$ for the adaptive.}
\label{fig:3testcase_a}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{For $t=5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_1500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{For $t=7.5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_c}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
}
}     
\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation.}
\label{fig:3testcase_d}
\end{figure}
\end{landscape}
\clearpage
